---
output: 
  pdf_document:
    template: preprint_template.tex
    fig_caption: true
    keep_tex: false
    citation_package: natbib
  word_document: 
    reference_docx: doc_template.docx
title: "Seasonal acclimation of copepod community thermal limits"
author:
  - name: Matthew Sasaki
    affiliation: University of Vermont
    location: 
  - name: Aly Rodgers
    affiliation: University of Vermont
    location: 
  - name: Chanchal Saratkar
    affiliation: University of Vermont
    location: 
  - name: Jamie Cull-Host
    affiliation: University of Vermont
    location: 
  - name: Sydney Sharp
    affiliation: University of Vermont
    location: 
  - name: Yuuki Real
    affiliation: University of Vermont
    location: 
  - name: Melissa Pespeni
    affiliation: University of Vermont
    location: 
abstract: "ABSTRACT HERE."
keywords: "keyword1, keyword2, keyword3"
contact: "**Correspondance**: matthew.sasaki@uvm.edu" 
current: "This preprint is current as of `r format(Sys.time(), '%B %d, %Y')`"
repo: "**Code**: https://github.com/ZoopEcoEvo/champlain_seasonality"
bibliography: references.bib
biblio-style: bib-style
geometry: margin=1in
fontsize: 10pt
graphics: yes
header-includes: 
  \usepackage{caption}    
  \captionsetup[figure]{font=small, margin=20pt, justification=centering}
  \captionsetup[table]{font=small, margin=20pt, justification=centering}
  \usepackage{float} \floatplacement{figure}{H} 
  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
---

```{r echo = F}
knitr::opts_chunk$set(fig.align = "center")
```

# Introduction

# Methods

## Statistical Analysis

# Results

Main figure (CTmax vs. date)

Ridge plot of collection frequencies + CTmax vs. Collection Temperature

Fecundity plot

Warming tolerance

Plasticity-tolerance trade-off plot

DLNM plot for diaptomids

```{r, figure, echo = F}
#| fig.cap = "CAPTION HERE."

plot(1)
#knitr::include_graphics("../Output/Figures/_PATH_") #Use this when filling in figures from analysis 
```

```{r, table, echo = F}
knitr::kable(x = 1, #Replace 1 with whatever object you want included as a table
      digits = 3, align = "c",
      caption = "CAPTION HERE")
```

# Discussion

Acclimation affects natural populations over seasonal timescales

Effects are shaped by trade-off with limits (as observed over other spatial / temporal / biological scales). Combined with patterns in warming tolerance, this suggests stronger effects on summer communities than winter communities (which may respond more via changes in phenology).

\newpage

```{=tex}
\beginsupplement
```
# Supplementary Material

Size plots

Frequency of pathogens / egg development

```{r supp-fig-1, echo = F}
#| fig.cap = "CAPTION HERE."

plot(1)
#knitr::include_graphics("../Output/Figures/_PATH_") #Use this when filling in figures from analysis 
```
