---
title: Seasonality in Lake Champlain Copepod Thermal Limits
date: "`r Sys.Date()`"
output: 
  html_document:
          code_folding: hide
          code_download: true
          toc: true
          toc_float: true
  github_document:
          html_preview: false
          toc: true
          toc_depth: 3
---

```{r to-do}
### To Do 

# Actual statistics for relationships between temperature and CTmax, size, and fecundity
# Pull residuals from CTmax ~ temperature model, and examine the change over time in lab and the relationship with fecundity

```


```{r setup, include=T, message = F, warning = F, echo = F}
knitr::opts_chunk$set(
  echo = knitr::is_html_output(),
  fig.align = "center",
  fig.path = "../Figures/markdown/",
  dev = c("png", "pdf"),
  message = FALSE,
  warning = FALSE,
  collapse = T
)

theme_matt = function(base_size = 18,
                      dark_text = "grey20"){
  mid_text <-  monochromeR::generate_palette(dark_text, "go_lighter", n_colours = 5)[2]
  light_text <-  monochromeR::generate_palette(dark_text, "go_lighter", n_colours = 5)[3]
  
  ggpubr::theme_pubr(base_family="sans") %+replace% 
    theme(
      panel.background  = element_rect(fill="transparent", colour=NA), 
      plot.background = element_rect(fill="transparent", colour=NA), 
      legend.background = element_rect(fill="transparent", colour=NA),
      legend.key = element_rect(fill="transparent", colour=NA),
      text = element_text(colour = mid_text, lineheight = 1.1),
      title = element_text(size = base_size * 1.5,
                           colour = dark_text),
      axis.text = element_text(size = base_size,
                               colour = mid_text),
      axis.title.x = element_text(size = base_size * 1.2,
                                  margin = unit(c(3, 0, 0, 0), "mm")),
      axis.title.y = element_text(size = base_size * 1.2,
                                  margin = unit(c(0, 5, 0, 0), "mm"), 
                                  angle = 90),
      legend.text = element_text(size=base_size * 0.9),
      legend.title = element_text(size = base_size * 0.9, 
                                  face = "bold"),
      plot.margin = margin(0.25, 0.25, 0.25, 0.25,"cm")
    )
}

theme_matt_facets = function(base_size = 18,
                             dark_text = "grey20"){
  mid_text <-  monochromeR::generate_palette(dark_text, "go_lighter", n_colours = 5)[2]
  light_text <-  monochromeR::generate_palette(dark_text, "go_lighter", n_colours = 5)[3]
  
  theme_bw(base_family="sans") %+replace% 
    theme(
      panel.grid = element_blank(),
      panel.background  = element_rect(fill="transparent", colour=NA), 
      plot.background = element_rect(fill="transparent", colour=NA), 
      legend.background = element_rect(fill="transparent", colour=NA),
      legend.key = element_rect(fill="transparent", colour=NA),
      text = element_text(colour = mid_text, lineheight = 1.1),
      strip.text.x = element_text(size = base_size),
      title = element_text(size = base_size * 1.5,
                           colour = dark_text),
      axis.text = element_text(size = base_size,
                               colour = mid_text),
      axis.title.x = element_text(size = base_size * 1.2,
                                  margin = unit(c(3, 0, 0, 0), "mm")),
      axis.title.y = element_text(size = base_size * 1.2,
                                  margin = unit(c(0, 5, 0, 0), "mm"), 
                                  angle = 90),
      legend.text = element_text(size=base_size * 0.9),
      legend.title = element_text(size = base_size * 0.9, 
                                  face = "bold"),
      plot.margin = margin(0.25, 0.25, 0.25, 0.25,"cm")
    )
}

species_cols = c("Leptodiaptomus minutus" = "#ffd029",
                 "Leptodiaptomus minutus male" = "#ffe896",
                 "Leptodiaptomus sicilis" = "#D86F29",
                 "Leptodiaptomus sicilis male" = "#E28C00",
                 "Skistodiaptomus oregonensis" = "#C5C35A",
                 "Skistodiaptomus oregonensis male" = "#e6e6aa", 
                 "Epischura lacustris juvenile" = "plum1", 
                 "Epischura lacustris male" = "plum3", 
                 "Epischura lacustris" = "plum4", 
                 "Limnocalanus macrurus" = "skyblue4", 
                 "Limnocalanus macrurus male" = "skyblue3", 
                 "Limnocalanus macrurus juvenile" = "skyblue", 
                 "Senecella calanoides" = "darkseagreen3")
```

## Temperature Variation 
Water temperatures in Lake Champlain reached a minimum in February. Sampling for this project began during the Spring warming period. Temperature variability (both ranges and variance) increase with temperature, but are strongly affected by the length of time period examined.    

```{r pulling-temp-data}
# Lake Champlain near Burlington, VT
siteNumber = "04294500"
ChamplainInfo = readNWISsite(siteNumber)
parameterCd = "00010"
startDate = "2023-01-01"
endDate = ""
#statCd = c("00001", "00002","00003", "00011") # 1 - max, 2 - min, 3 = mean

# Constructs the URL for the data wanted then downloads the data
url = constructNWISURL(siteNumbers = siteNumber, parameterCd = parameterCd, 
                       startDate = startDate, endDate = endDate, service = "uv")

temp_data = importWaterML1(url, asDateTime = T) %>% 
  mutate("date" = as.Date(dateTime)) %>% 
  select(date, "temp" = X_00010_00000)


## Daily values
daily_temp_data = temp_data %>%
  ungroup() %>% 
  group_by(date) %>% 
  summarise(mean_temp = mean(temp),
            med_temp = median(temp),
            var_temp = var(temp), 
            min_temp = min(temp), 
            max_temp = max(temp)) %>% 
  mutate("range_temp" = max_temp - min_temp)

daily_plot = daily_temp_data %>% 
  pivot_longer(cols = c(-date),
               names_to = "parameter", 
               values_to = "temp") %>% 
  ggplot(aes(x = date, y = temp, colour = parameter)) + 
  geom_line(linewidth = 1) + 
  scale_colour_manual(values = c(
    "mean_temp" = "olivedrab3",
    "med_temp" = "seagreen3",
    "max_temp" = "tomato",  
    "min_temp" = "dodgerblue",
    "range_temp" = "goldenrod3",
    "var_temp" = "darkgoldenrod1"
  )) + 
  scale_x_continuous(breaks = as.Date(c("2023-01-01", "2023-04-01", "2023-07-01"))) + 
  ggtitle("Daily Values") + 
  labs(y = "Temperature (°C)",
       x = "") + 
  theme_bw(base_size = 20) + 
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(angle = 270, hjust = 0, vjust = 0.5))
```

```{r predictors-function}
## Defining the function to get predictor values for periods of different lengths
get_predictors = function(daily_values, raw_temp, n_days){
  prefix = str_replace_all(xfun::numbers_to_words(n_days), pattern = " ", replacement = "-")
  
  mean_values = daily_values %>% 
    ungroup() %>% 
    mutate(mean_max = slide_vec(.x = max_temp, .f = mean, .before = n_days, .complete = T),
           mean_min = slide_vec(.x = min_temp, .f = mean, .before = n_days, .complete = T),
           mean_range = slide_vec(.x = range_temp, .f = mean, .before = n_days, .complete = T)) %>% 
    select(date, mean_max, mean_min, mean_range) %>% 
    rename_with( ~ paste(prefix, "day", .x, sep = "_"), .cols = c(-date))
  
  period_values = raw_temp %>% 
    mutate(mean = slide_index_mean(temp, i = date, before = days(n_days), 
                                   na_rm = T),
           max = slide_index_max(temp, i = date, before = days(n_days), 
                                 na_rm = T),
           min = slide_index_min(temp, i = date, before = days(n_days),
                                 na_rm = T),
           med = slide_index_dbl(temp, .i = date, .before = days(n_days), 
                                    na_rm = T, .f = median),
           var = slide_index_dbl(temp, .i = date, .before = days(n_days), 
                                 .f = var),
           range = max - min) %>%  
    select(-temp) %>%  
    distinct() %>% 
    rename_with( ~ paste(prefix, "day", .x, sep = "_"), .cols = c(-date))%>% 
    inner_join(mean_values, by = c("date")) %>%  
    drop_na()
  
  return(period_values)
}
```


```{r predictors-and-plots, fig.width=12, fig.height=5}
## Getting predictor variables for different periods

### ONE WEEK
week_temps = get_predictors(daily_values = daily_temp_data, 
                            raw_temp = temp_data, 
                            n_days = 7)

week_plot = week_temps %>% 
  pivot_longer(cols = c(-date),
               names_to = "parameter", 
               values_to = "temp") %>% 
  filter(parameter %in% c("seven_day_mean",
                          "seven_day_med",
                          "seven_day_max", 
                          "seven_day_min", 
                          "seven_day_var",
                          "seven_day_range")) %>% 
  mutate(parameter = paste(word(parameter, start = 3, sep = fixed("_")), "_temp", sep = "")) %>% 
  ggplot(aes(x = date, y = temp, colour = parameter)) + 
  geom_line(linewidth = 1) + 
  scale_colour_manual(values = c(
    "mean_temp" = "olivedrab3",
    "med_temp" = "seagreen3",
    "max_temp" = "tomato",  
    "min_temp" = "dodgerblue",
    "range_temp" = "goldenrod3",
    "var_temp" = "darkgoldenrod1"
  )) + 
  scale_x_continuous(breaks = as.Date(c("2023-01-01", "2023-04-01", "2023-07-01"))) + 
  ggtitle("One Week") + 
  labs(y = "Temperature (°C)",
       x = "") + 
  theme_bw(base_size = 20) + 
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(angle = 270, hjust = 0, vjust = 0.5))


### TWO WEEKS
two_week_temps = get_predictors(daily_values = daily_temp_data, 
                                raw_temp = temp_data, 
                                n_days = 14)

two_week_plot = two_week_temps %>% 
  pivot_longer(cols = c(-date),
               names_to = "parameter", 
               values_to = "temp") %>% 
  filter(parameter %in% c("fourteen_day_mean",
                          "fourteen_day_med",
                          "fourteen_day_max", 
                          "fourteen_day_min", 
                          "fourteen_day_var",
                          "fourteen_day_range")) %>% 
  mutate(parameter = paste(word(parameter, start = 3, sep = fixed("_")), "_temp", sep = "")) %>% 
  ggplot(aes(x = date, y = temp, colour = parameter)) + 
  geom_line(linewidth = 1) + 
  scale_colour_manual(values = c(
    "mean_temp" = "olivedrab3",
    "med_temp" = "seagreen3",
    "max_temp" = "tomato",  
    "min_temp" = "dodgerblue",
    "range_temp" = "goldenrod3",
    "var_temp" = "darkgoldenrod1"
  )) + 
  scale_x_continuous(breaks = as.Date(c("2023-01-01", "2023-04-01", "2023-07-01"))) + 
  ggtitle("Two Weeks") + 
  labs(y = "Temperature (°C)",
       x = "") + 
  theme_bw(base_size = 20) + 
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(angle = 270, hjust = 0, vjust = 0.5))


### FOUR WEEKS
four_week_temps = get_predictors(daily_values = daily_temp_data, 
                                 raw_temp = temp_data, 
                                 n_days = 28)

four_week_plot = four_week_temps %>% 
  pivot_longer(cols = c(-date),
               names_to = "parameter", 
               values_to = "temp") %>% 
  filter(parameter %in% c("twenty-eight_day_mean",
                          "twenty-eight_day_med",
                          "twenty-eight_day_max", 
                          "twenty-eight_day_min", 
                          "twenty-eight_day_var",
                          "twenty-eight_day_range")) %>% 
  mutate(parameter = paste(word(parameter, start = 3, sep = fixed("_")), "_temp", sep = "")) %>% 
  ggplot(aes(x = date, y = temp, colour = parameter)) + 
  geom_line(linewidth = 1) + 
  scale_colour_manual(values = c(
    "mean_temp" = "olivedrab3",
    "med_temp" = "seagreen3",
    "max_temp" = "tomato",  
    "min_temp" = "dodgerblue",
    "range_temp" = "goldenrod3",
    "var_temp" = "darkgoldenrod1"
  )) + 
  scale_x_continuous(breaks = as.Date(c("2023-01-01", "2023-04-01", "2023-07-01"))) + 
  ggtitle("Four Weeks") + 
  labs(y = "Temperature (°C)",
       x = "") + 
  theme_bw(base_size = 20) + 
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(angle = 270, hjust = 0, vjust = 0.5))


### EIGHT WEEKS
eight_week_temps = get_predictors(daily_values = daily_temp_data, 
                                  raw_temp = temp_data, 
                                  n_days = 56)

eight_week_plot = eight_week_temps %>% 
  pivot_longer(cols = c(-date),
               names_to = "parameter", 
               values_to = "temp") %>% 
  filter(parameter %in% c("fifty-six_day_mean",
                          "fifty-six_day_med",
                          "fifty-six_day_max", 
                          "fifty-six_day_min", 
                          "fifty-six_day_var",
                          "fifty-six_day_range")) %>% 
  mutate(parameter = paste(word(parameter, start = 3, sep = fixed("_")), "_temp", sep = "")) %>% 
  ggplot(aes(x = date, y = temp, colour = parameter)) + 
  geom_line(linewidth = 1) + 
  scale_colour_manual(values = c(
    "mean_temp" = "olivedrab3",
    "med_temp" = "seagreen3",
    "max_temp" = "tomato",  
    "min_temp" = "dodgerblue",
    "range_temp" = "goldenrod3",
    "var_temp" = "darkgoldenrod1"
  )) + 
  scale_x_continuous(breaks = as.Date(c("2023-01-01", "2023-04-01", "2023-07-01"))) + 
  ggtitle("Eight Weeks") + 
  labs(y = "Temperature (°C)",
       x = "") + 
  theme_bw(base_size = 20) + 
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(angle = 270, hjust = 0, vjust = 0.5))

ggarrange(daily_plot, week_plot, two_week_plot, four_week_plot, eight_week_plot, 
          common.legend = T, nrow = 1, legend = "bottom")
```


```{r pulling-predictors}
## Combine data, then pull out values for each collection date
date_list = as.Date(unique(full_data$collection_date))

temp_predictors = daily_temp_data %>% 
  full_join(week_temps, by = c("date")) %>% 
  full_join(two_week_temps, by = c("date")) %>% 
  full_join(four_week_temps, by = c("date")) %>% 
  full_join(eight_week_temps, by = c("date")) %>% 
  filter(date %in% date_list)
```

A set of predictors variables were assembled from the continuous temperature data set based on conditions during the day of collection, the week before collections, and the preceding two, four, and eight week periods. This is a preliminary analysis for now. Shown here are the top three factors. Species with no significant predictor or limited collection date distributions were excluded. 

```{r predictor-correlations}
corr_vals = full_data %>%  
  filter(sp_name != "Senecella calanoides") %>%
  filter(sp_name != "Limnocalanus macrurus") %>%
  mutate(collection_date = as.Date(collection_date)) %>% 
  full_join(temp_predictors, join_by(collection_date == date)) %>% 
  pivot_longer(cols = c(collection_temp, mean_temp:tail(names(.), 1)),
               values_to = "value", 
               names_to = "predictor") %>%  
  group_by(sp_name, predictor) %>% 
  summarise(correlation = cor.test(ctmax, value)$estimate,
            p.value = cor.test(ctmax, value)$p.value,
            ci_low = cor.test(ctmax, value)$conf.int[1],
            ci_high = cor.test(ctmax, value)$conf.int[2]) %>% 
  mutate(sig = ifelse(p.value <0.05, "Sig.", "Non Sig."))

corr_vals %>%  
  filter(sig == "Sig.") %>% 
  drop_na(correlation) %>% 
  group_by(sp_name) %>%
  arrange(desc(correlation)) %>% 
  slice_head(n = 3) %>% 
  select("Species" = sp_name, "Predictor" = predictor, "Correlation" = correlation, "P-Value" = p.value) %>% 
  knitr::kable(align = "c")
```

## Trait Variation 
```{r ctmax-and-size-sum-plot, fig.width=20, fig.height=5}
ctmax_plot = full_data %>% 
  mutate( #sp_name = str_replace(sp_name, pattern = " ",
    #                              replacement = "\n"),
    sp_name = fct_reorder(sp_name, ctmax, mean)) %>% 
  ggplot(aes(y = sp_name, x = ctmax)) + 
  geom_point(aes(colour= sp_name_sub),
             position = position_dodge(width = 0.3),
             size = 4) + 
  scale_colour_manual(values = species_cols) + 
  xlab(NULL) + 
  labs(y = "",
       x = "CTmax (°C)",
       colour = "Group") + 
  theme_matt() + 
  theme(legend.position = "none")

size_plot = full_data %>% 
  mutate(sp_name = fct_reorder(sp_name, ctmax, mean)) %>% 
  ggplot(aes(y = sp_name, x = size)) + 
  geom_point(aes(colour= sp_name_sub),
             position = position_dodge(width = 0.3),
             size = 4) + 
  scale_colour_manual(values = species_cols) + 
  labs(x = "Prosome Length (mm)",
       y = "", 
       colour = "Group") + 
  guides(color = guide_legend(ncol = 1)) +
  theme_matt(base_size = ) + 
  theme(legend.position = "right",
        axis.text.y = element_blank(),
        plot.margin = margin(0, 0, 0, 0,"cm"))

trait_plot = ctmax_plot + size_plot
trait_plot
```

```{r ctmax-and-size-histograms, fig.width=7, fig.height=21, include = F}
ggplot(full_data, aes(x = size, fill = sp_name_sub)) + 
  facet_wrap(.~sp_name_sub, ncol = 1) + 
  geom_histogram(binwidth = 0.05) + 
  scale_fill_manual(values = species_cols) + 
  labs(x = "Prosome length (mm)") + 
  theme_matt_facets() + 
  theme(legend.position = "none")

ggplot(full_data, aes(x = ctmax, fill = sp_name_sub)) + 
  facet_wrap(.~sp_name_sub, ncol = 1) + 
  geom_histogram(binwidth = 1) + 
  scale_fill_manual(values = species_cols) + 
  labs(x = "CTmax (°C)") + 
  theme_matt_facets() + 
  theme(legend.position = "none")
```

```{r fecundity-histogram, fig.width=7, fig.height=10}
full_data %>%  
  drop_na(fecundity) %>%  
  ggplot(aes(x = fecundity, fill = sp_name_sub)) + 
  facet_wrap(.~sp_name_sub, ncol = 1) + 
  geom_histogram(binwidth = 2) + 
  scale_fill_manual(values = species_cols) + 
  labs(x = "Fecundity (# Eggs)") +
  theme_matt_facets() + 
  theme(legend.position = "none")
```

### Variation with temperature 

```{r trait-coll-temp-plots, fig.width=15, fig.height=10}
ctmax_temp = ggplot(full_data, aes(x = collection_temp, y = ctmax, colour = sp_name)) + 
  geom_smooth(method = "lm", linewidth = 3) +
  geom_point(size = 3) + 
  labs(x = "Collection Temperature (°C)", 
       y = "CTmax (°C)",
       colour = "Group") + 
  scale_colour_manual(values = species_cols) + 
  theme_matt() + 
  theme(legend.position = "right")

size_temp = ggplot(filter(full_data, sex != "juvenile"), aes(x = collection_temp, y = size, colour = sp_name)) + 
  geom_smooth(method = "lm", linewidth = 3) +
  geom_point(size = 3) + 
  labs(x = "Collection Temperature (°C)", 
       y = "Length (mm)",
       colour = "Group")  + 
  scale_colour_manual(values = species_cols) + 
  theme_matt() + 
  theme(legend.position = "right")

wt_temp = ggplot(full_data, aes(x = collection_temp, y = warming_tol, colour = sp_name)) + 
  geom_smooth(method = "lm", linewidth = 3) +
  geom_point(size = 3) + 
  labs(x = "Collection Temperature (°C)", 
       y = "Warming Tolerance (°C)",
       colour = "Group")  + 
  scale_colour_manual(values = species_cols) + 
  theme_matt() + 
  theme(legend.position = "right")

eggs_temp = ggplot(full_data, aes(x = collection_temp, y = fecundity, colour = sp_name)) + 
  geom_smooth(method = "lm", linewidth = 3) +
  geom_point(size = 3) + 
  labs(x = "Collection Temperature (°C)", 
       y = "Fecundity (# Eggs)",
       colour = "Group")  + 
  scale_colour_manual(values = species_cols) + 
  theme_matt() + 
  theme(legend.position = "right")

ggarrange(ctmax_temp, size_temp, wt_temp, eggs_temp, 
          common.legend = T, legend = "right")
```

```{r ctmax-coll-temp-model}
ctmax_temp.model = lm(data = full_data, ctmax ~ collection_temp * sp_name)

knitr::kable(car::Anova(ctmax_temp.model))

ctmax_resids = cbind(full_data, "resids" = ctmax_temp.model$residuals)
```

```{r fig.width=15, fig.height=10}
ggplot(ctmax_resids, aes(x = days_in_lab, y = resids, colour = sp_name)) + 
  facet_wrap(sp_name~.) + 
  geom_point(size = 4) + 
  geom_smooth(method = "lm", se = F, linewidth = 2) + 
  scale_x_continuous(breaks = c(0:3)) + 
  labs(x = "Days in lab", 
       y = "CTmax Residuals") + 
  scale_colour_manual(values = species_cols) + 
  theme_matt_facets() + 
  theme(legend.position = "none")
```

## Sex and stage variation in thermal limits 
Previous sections have generally lumped juvenile, female, and male individuals together. There may be important stage- or sex-specific differences in CTmax though. For several species, we have measurements for individuals in different stages or of different sexes. 

```{r}
sex_sample_sizes = ctmax_resids %>%  
  group_by(sp_name, sex) %>%  
  summarise(num = n()) %>%  
  pivot_wider(id_cols = sp_name,
              names_from = sex, 
              values_from = num,
              values_fill = 0) %>% 
  select("Species" = sp_name, "Juvenile" = juvenile, "Female" = female, "Male" = male)

knitr::kable(sex_sample_sizes, align = "c")

```

The female-male and female-juvenile comparisons show that there are generally no differences in thermal limits between these groups. 

```{r fig.width=7, fig.height=7}
ctmax_resids %>% 
  filter(sp_name %in% filter(sex_sample_sizes, Male > 0)$Species & 
           sex != "juvenile") %>% 
  ggplot(aes(x = sex, y = resids, colour = sp_name, group = sp_name)) + 
  facet_wrap(sp_name~., ncol = 2) + 
  geom_smooth(method = "lm", se = F, linewidth = 1) + 
  geom_point(size = 3,
             alpha = 0.5,
             position = position_jitter(height = 0, width = 0.05)) +  
  labs(x = "Sex", 
       y = "CTmax Residuals") + 
  scale_colour_manual(values = species_cols) + 
  theme_bw(base_size = 18) + 
  theme(legend.position = "none", 
        panel.grid = element_blank())
```

```{r fig.width=3, fig.height=6}
ctmax_resids %>% 
  filter(sp_name %in% filter(sex_sample_sizes, Juvenile > 0)$Species & 
           sex != "male") %>% 
  ggplot(aes(x = sex, y = resids, colour = sp_name, group = sp_name)) + 
  facet_wrap(sp_name~., ncol = 1) + 
  geom_smooth(method = "lm", se = F, linewidth = 1) + 
  geom_point(size = 3,
             alpha = 0.5,
             position = position_jitter(height = 0, width = 0.05)) +  
  labs(x = "Sex", 
       y = "CTmax (°C)") + 
  scale_colour_manual(values = species_cols) + 
  theme_bw(base_size = 18) + 
  theme(legend.position = "none", 
        panel.grid = element_blank())
```

## Trait Correlations 

```{r fig.width=10, fig.height=7}
ggplot(full_data, aes(x = size, y = ctmax, colour = sp_name)) + 
  geom_smooth(data = full_data, 
              aes(x = size, y = ctmax),
              method = "lm", 
              colour ="black", 
              linewidth = 2.5) + 
  geom_smooth(method = "lm", se = F, linewidth = 2) + 
  geom_point(size = 4) + 
  labs(x = "Length (mm)", 
       y = "CTmax (°C)") + 
  scale_colour_manual(values = species_cols) + 
  theme_matt() + 
  theme(legend.position = "right")
```

```{r fig.width=10, fig.height=7, include = F}
ggplot(ctmax_resids, aes(x = size, y = resids, colour = sp_name)) + 
  geom_smooth(data = ctmax_resids, 
              aes(x = size, y = resids),
              method = "lm", 
              colour ="black", 
              linewidth = 2.5) + 
  geom_smooth(method = "lm", se = F, linewidth = 2) + 
  geom_point(size = 4) + 
  labs(x = "Length (mm)", 
       y = "CTmax (°C)") + 
  scale_colour_manual(values = species_cols) + 
  theme_matt() + 
  theme(legend.position = "right")
```


```{r fig.width=10, fig.height=7}
ggplot(ctmax_resids, aes(x = size, y = fecundity, colour = sp_name)) + 
  geom_smooth(method = "lm", se = F, linewidth = 2) + 
  geom_point(size = 4) + 
  labs(x = "Prosome length (mm)", 
       y = "Fecundity (# Eggs)") + 
  scale_colour_manual(values = species_cols) + 
  theme_matt() + 
  theme(legend.position = "right")
```

```{r fig.width=10, fig.height=7}
ggplot(ctmax_resids, aes(x = resids, y = fecundity, colour = sp_name)) + 
  geom_smooth(method = "lm", se = F, linewidth = 2) + 
  geom_point(size = 4) + 
  labs(x = "CTmax Residuals", 
       y = "Fecundity (# Eggs)") + 
  scale_colour_manual(values = species_cols) + 
  theme_matt() + 
  theme(legend.position = "right")
```


